---
title: "FMEA"
author: "Tony Gojanovic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## FMEA Package Overview

This simple package graphs output from an Failure Mode Effects (FMEA) onto a hazard or disutility graph (failure occurrence by failure severity) and a controls graph (failure detection by failure occurrence).  It also provides risk zones on the hazard graph along with labels of items from your FMEA worksheet.

## Package Usage

This package imports a file (usually in Excel) and then plots scatterplot type graphs to understand risk.  The code can be incorporated into a markdown report or however desired.

## R Packages

The following R packages are used:

```{r eval=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(ggrepel)
```

## Minimum Data Requirements

The data table must have the following field names:

item_no  
severity  
occurrence
detection  

Of course, there will be other fields included.  See the example data sheet called **fmea_working_file.xls** for a complete listing of fields and names (found under inst\ extdata).

## Making the graphs

The following code shows how the graphs can be made:

```{r eval=FALSE,warning=FALSE,message=FALSE}

library(ggplot2)
library(dplyr)
library(ggrepel)

# If importing an Excel worksheet, the following code chunk is to be used (based on your working directory).

library(readxl)
fmea_working_file <- read_excel("~/Data/Statistical Projects/R Projects/FMEA/inst/extdata/fmea_working_file.xls")

# To make the hazard or disutility graph (with risk zones)

risk_disutility(fmea_working_file)

# To make the risk controls graph (no risk zones)

risk_controls(fmea_working_file)

```

The graphs can then be incorporated into a risk report or presentation as needed.

## References

Zone configurations for the hazard or disutility graph is based on the following:

Carlson, Carl S., *Effective FMEAs: Achieving Safe, Reliable, and Economical Products and Processes Using Failure Mode and Effects Analysis*, John Wiley and Sons, New York, 2012, p. 164. 

Code can be altered to provide differing risk zone configurations.

